Supplementary Materials

### 2023-07-03 manuscript/supplementary.tex
minor ms changes

    \textbf{Model} & \textbf{Track type} & \textbf{Pop.} & \textbf{B' $R_\text{LOO}^2$} & \textbf{B' $R_\text{IS}^2$} & \textbf{B $R_\text{IS}^2$} & \textbf{B' $\hat{\mu} \times 10^{-8}$} & \textbf{B $\hat{\mu} \times 10^{-8}$} \\[0.5ex] 

@@

where each $B_i = f(X_i | \Psi)$ for some data $X_i$ (i.e. the recombinaton map
and annotation model) and parameters $\Psi$. To compare our models and assess
model goodness-of-fit, we use the out-sample $R_\text{LOO}^2$ which is
calculated by fitting the genome-wide model leaving one chromosome out, and
calculating the residual variance between predictions and observed values for
this out-sample chromosome.

@@

This back-of-the-envelope calculation finds that the upper bound of $R^2$ would
be around 67\% for Yoruba, and 64\% for European and Han Chinese models (Figure
\ref{suppfig:drift_r2} This rough approximation assumes constant demography,
which for bottlenecked out-of-Africa populations assumes that the variance in
coalescence times is determined entirely by reducing the effective population
size. However, the variance in coalescence times is \emph{higher} in
bottlenecked populations (CEU and CHB) compared to Yoruba, which we confirm
with simple simulations using the \texttt{OutOfAfrica\_3G09} model from
\texttt{stdpopsim} \parencite{Gutenkunst2009-pg,Adrion2020-cf}. This higher
than expected variance would inflate $SS_\text{res}$, which would decrease
$R_\text{drift}^2$, bringing it closer to the observed $R_\text{LOO}^2$. A more
accurate approximation of the $R_\text{drift}^2$ could be found with
simulations with more realistic demography and varying coalescence rates along
the genome.

@@

>>>>

    \textbf{Model} & \textbf{Track type} & \textbf{Pop.} & \textbf{B' $R_\text{LOCO}^2$} & \textbf{B' $R_\text{IS}^2$} & \textbf{B $R_\text{IS}^2$} & \textbf{B' $\hat{\mu} \times 10^{-8}$} & \textbf{B $\hat{\mu} \times 10^{-8}$} \\[0.5ex] 

@@

where each $B_i = f(X_i | \Psi)$ for some data $X_i$ (i.e. the recombinaton map
and annotation model) and parameters $\Psi$. To compare our models and assess
model goodness-of-fit, we use the out-sample $R_\text{LOCO}^2$ which is
calculated by fitting the genome-wide model leaving one chromosome out, and
calculating the residual variance between predictions and observed values for
this out-sample chromosome.

@@

This back-of-the-envelope calculation finds that the upper bound of $R^2$ would
be around 67\% for Yoruba, and 64\% for European and Han Chinese models (Figure
\ref{suppfig:drift_r2} This rough approximation assumes constant demography,
which for bottlenecked out-of-Africa populations assumes that the variance in
coalescence times is determined entirely by reducing the effective population
size. However, the variance in coalescence times is \emph{higher} in
bottlenecked populations (CEU and CHB) compared to Yoruba, which we confirm
with simple simulations using the \texttt{OutOfAfrica\_3G09} model from
\texttt{stdpopsim} \parencite{Gutenkunst2009-pg,Adrion2020-cf}. This higher
than expected variance would inflate $SS_\text{res}$, which would decrease
$R_\text{drift}^2$, bringing it closer to the observed $R_\text{LOCO}^2$. A more
accurate approximation of the $R_\text{drift}^2$ could be found with
simulations with more realistic demography and varying coalescence rates along
the genome.

@@

\begin{figure}[htbp]
    \label{suppfig:dfe-pop-smallgrid}
  \centering
  \includegraphics[width=0.6\textwidth]{figures/supplementary/phastcons_priority_pop_dfe_smallselgrid.pdf}
  \caption{The DFE for the PhastCons Priority model, fit with a smaller DFE grid from 
  $\mu \in \{10^{-8}, 10^{-7}, \ldots, 10^{-2}\}$.}
\end{figure}
